Implementation and assessment of tools for integrating forest roads into projections of the cumulative effects of disturbance on wildlife

### 2024-03-15 analysis/paper/paper.Rmd
Ongoing grade penalty work

# re-run projections for just the small area with different parameters
mstProj <- projectAll(tsbs = tsb, paramTable = paramTable,
                      costSurface = tsaCost,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"))

ilcpProj <- projectAll(tsbs = tsb,
                      paramTable = paramTable %>% 
                        filter(sampleType == "regular") %>% 
                        mutate(method = "ilcp"),
                      costSurface = tsaCost,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"))

>>>>

# re-run projections for just the small area with different parameters
mstProj <- projectAll(tsbs = tsb, paramTable = paramTable,
                      costSurface = tsaCost,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"),roadsInCost = F)

ilcpProj <- projectAll(tsbs = tsb,
                      paramTable = paramTable %>% 
                        filter(sampleType == "regular") %>% 
                        mutate(method = "ilcp"),
                      costSurface = tsaCost,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"),roadsInCost = F)
